Evaluating the Performance and Energy Efficiency of COSMO-ART, a Fully Online Coupled Model System with Numerical Weather Forecast and Chemical Transport Models

### 2014-04-01 trunk/paper_enahpc14/paper.tex
updates paper and tidy files up; starts redaction of Section 1.
Manuel's changes

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\RequirePackage{fix-cm}
%
\documentclass[twocolumn]{svjour3}           % twocolumn
%
\smartqed % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[round, sort&compress, numbers]{natbib}
%
\DeclareRobustCommand\IPCClongname{}
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

\title{Evaluating the performance  and energy efficiency of COSMO-ART,
  a fully online coupled model  system composed of a numerical weather
  forecast model  and a  chemical transport model.   \thanks{Grants or
    other notes  about the  article that should  go on the  front page
    should be placed here.}}
%\subtitle{Write here subtitle}

@@

\author{J.Charles \and W.Sawyer \and M.Dolz \and C.Malossi}

@@

\institute{Dr. Joseph Charles \at Swiss National Supercomputing Centre
  (CSCS)\\ CH-6900  Lugano, Switzerland  \\ Tel: +41  (0) 91  610 8216
  \\ \email{joseph.charles@cscs.ch} \and Dr.  William Sawyer \at Swiss
  National Supercomputing Centre  (CSCS)\\ CH-6900 Lugano, Switzerland
  \\ Tel:  +41 (0) 91 610 8229  \\ \email{william.sawyer@cscs.ch} \and
  Dr.  Manuel Dolz \at University of Hamburg \\ 20148 Hamburg, Germany
  \\         Tel:         +49         (0)        40         460094-404
  \\ \email{manuel.dolz@informatik.uni-hamburg.de}  \and Dr. Cristiano
  Malossi  \at  IBM  Zurich  Research Laboratory  \\  CH-8000  Zurich,
  Switzerland     \\     Tel:      +41     (0)     44     724     8616
  \\ \email{ACM@zurich.ibm.com}}

@@

\section{The operational COSMO-ART}
\label{sec:1}
\subsection{Model description}
\label{subsec:1.1}
\input{Subsec_1.1:Model_Description.tex}

\subsection{Model setup}
\label{subsec:1.2}
\input{Subsec_1.2:Model_Setup.tex}

@@

\section{Power measurement systems}
\label{sec:3}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\RequirePackage{fix-cm}
%
\documentclass[twocolumn]{svjour3}           % twocolumn
%
\smartqed % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[round, sort&compress, numbers]{natbib}

\usepackage{multirow}
\usepackage{graphicx}
\usepackage{units}
\usepackage{color}

\usepackage{xspace}
\newcommand{\pmlib}{\texttt{pmlib}\xspace}

%
\DeclareRobustCommand\IPCClongname{}
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

\title{Evaluating the Performance  and Energy Efficiency of COSMO-ART,
  a Fully Online Coupled Model System with Numerical Weather
    Forecast and Chemical Transport Models }
 % \thanks{This work was supported 
 %   by the EU Project FP7 318793 ``EXA2GREEN''}}
%\subtitle{Write here subtitle}

@@

\author{Joseph~Charles \and William~Sawyer \and Manuel~F.~Dolz \and Cristiano~Malossi}

@@

\institute{J.~Charles, W.~Sawyer 
	\at Swiss National Supercomputing Centre (CSCS)
	\\ CH-6900 Lugano, Switzerland  
	%\\ Tel: +41  (0) 91  610 8216
 	\\ E-mails:~{\{joseph.charles,william.sawyer\}@cscs.ch} 
        %\and Dr.  William Sawyer 
        %\at Swiss National Supercomputing Centre  (CSCS)
        %\\ CH-6900 Lugano, Switzerland
        %\\ Tel:  +41 (0) 91 610 8229  
        %\\ \email{william.sawyer@cscs.ch} 
        \and M.~F.~Dolz 
        \at Dept. of Informatics, University of Hamburg
	\\ D-22.527 Hamburg, Germany
        %\\ Tel: +49 (0) 40 460094-404
        \\ \email{manuel.dolz@informatik.uni-hamburg.de}  
        \and C.~Malossi  
        \at IBM Zurich Research Laboratory 
        \\  CH-8000 Zurich, Switzerland
        %\\  Tel: +41 (0) 44 724 8616
        \\ \email{ACM@zurich.ibm.com}}

@@

\section{The COSMO-ART model system}
\label{sec:1}
\input{Sec1:COSMO-ART.tex}

@@

\section{Power measurement systems}
\label{sec:3}
\input{power-measurement.tex}
